---
title: "Hello, Quarto"
subtitle: "Cross-language coding"
author: "Julian Oliver Dörr"
format: gfm
editor: source
engine: knitr
---

## Quarto
[Quarto](https://quarto.org/) weaves together narrative text and code to produce elegantly formatted output. Most interestingly, Quarto executes code written in different languages. The following gives an illustration of cross-language coding in Quarto (here using **`R`** and **`Python`** - other languages are supported as well).

## Cross-language coding

### R

**`R`** code chunks are written and executed just as we would do it in R Markdown. So, for users of R Markdown this should be very familiar. 

```{r}
#| label: load-packages
#| include: false
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, palmerpenguins, reticulate)
```

```{r}
#| label: plot-penguins
#| warning: false
#| echo: true
data(penguins, package = "palmerpenguins")
penguins <- penguins[complete.cases(penguins),]

ggplot(penguins, 
       aes(x = flipper_length_mm, y = bill_length_mm)) +
  geom_point(aes(color = species, shape = species)) +
  scale_color_manual(values = c("darkorange","purple","cyan4")) +
  labs(
    title = "Flipper and bill length",
    subtitle = "Dimensions for penguins at Palmer Station LTER",
    x = "Flipper length (mm)", y = "Bill length (mm)",
    color = "Penguin species", shape = "Penguin species"
  ) +
  theme_light()
```

### Python

The beauty comes into play when we add **`Python`** chunks of code.

```{python}
#| label: load-modules
#| include: false
import pandas as pd
import numpy as np
from sklearn.model_selection import train_test_split
from sklearn.ensemble import RandomForestClassifier
from sklearn.metrics import classification_report
```

```{python}
#| label: R-to-python
#| warning: false
#| echo: true
penguins = r.penguins
penguins.head(3)
```

We simply switched from **`R`** to **`Python`** working on the *penguins* data set.

Now, let us train a simple classifier using the `scikit-learn` module in **`Python`**.


```{python}
#| label: classify-penguins
#| warning: false
#| echo: true
y = penguins['species']
X = penguins[['bill_length_mm',  'bill_depth_mm',  'flipper_length_mm', 'body_mass_g']]
X_train, X_test, y_train, y_test = train_test_split(X, y, test_size = 0.2, random_state = 333)

classifier = RandomForestClassifier().fit(X_train, y_train)
y_test_pred = classifier.predict(X_test)

print(classification_report(y_test, y_test_pred))
```

## Conclusion

Great, with Quarto it is possible to write reports, presentations, ... using different languages. Here, we have made use of **`R`**'s `tidyverse` for data preprocessing and visualization and **`Python`**'s Machine Learning frameworks (`scikit-learn` in this example). So Quarto really enables you to pick the best of both worlds.
